Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-19 paper.tex
fixing Apendix A tables

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce. U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e. those that can have a higher influence on the creation of that cluster.
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
% Antonio - explained. ;)

@@

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression (LR)}:
 Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictor) over the range of values in the dataset. 
In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.

This method of regression provides an adequate and interpretable description of 
how the input affects the output as it models the dependent variable as a linear 
function of the independent variables. Moreover, the linear relation can be 
solved using the least squares method, that minimises the error between the 
actual data and the regression line \cite{McClendon2015}.

@@

The objective is finding the most appropriate forecasting method that minimises 
the error between the obtained forecast and the actual sales for each new book 
published.

@@

  \item \emph{Root relative squared error} (RRSE):
        \begin{equation}\label{eq:RRSE}
            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
        \end{equation}
\end{itemize}
where $o_i$ is the actual value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.

@@

kNN is the fastest method used in this study in terms of training time, as it is the simplest method. However, the model is slow when classifying large number of 
training examples, and it exhibits a poor generalisation ability since it does not 
learn anything from the training data.

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
\hline 
kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
\hline 
LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
\hline 
kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
\hline 
LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
\hline 
kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
\hline 
LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
\hline 
SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
\hline 
kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
\hline 
LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
\hline 
kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
\hline 
LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
\hline 
kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
\hline 
LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
\hline 
kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 75.1 $\pm$0.26 & 15.61 $\pm$7.19 & 26.83 $\pm$13.36 & 47.38 $\pm$20.10 & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
\hline 
LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & 25.49 $\pm$11.63 & 47.97 $\pm$18.85 & 60.28 $\pm$30.62 & 0.0002 $\pm$0.0004\tabularnewline
\hline 
SVM & 81.8 $\pm$0.21 & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 86.0 $\pm$0.19 & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
\hline 
kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 85.5 $\pm$0.19 & 13.66 $\pm$6.47 & 22.51 $\pm$11.03 & 41.38 $\pm$17.87 & 52.20 $\pm$27.09 & 0.026 $\pm$0.0019\tabularnewline
\hline 
LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
\hline 
SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

>>>>

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce. U-Matrix graph, together with the projection of variables into separate planes, the so-called component planes analysis (that SOM yields), will aid an expert to identify the most relevant features on every cluster, i.e. those with a higher influence on the creation of that cluster.
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
% Antonio - explained. ;)

@@

Thus, in this research five forecasting methods, based on the State of the Art literature 
review (see Section \ref{sec:soa}) 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool have been chosen, as these methods are widely known, and could be very helpful for practitioners to reproduce experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression (LR)}:
 Linear Regression \cite{Cohen2003,Yan2009,Rencher2102,EnkeT05} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictors) over the range of values in the dataset. 
In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.

This method of regression provides an adequate and interpretable description of 
how the input affects the output as it models the dependent variable as a linear 
function of the independent variables. Moreover, the linear relation can be 
solved using the least squares method, that minimises the error between the 
current data and the regression line \cite{McClendon2015}.

@@

The objective is finding the most appropriate forecasting method that minimises 
the error between the obtained forecast and the current sales for each new book 
published.

@@

  \item \emph{Root relative squared error} (RRSE):
        \begin{equation}\label{eq:RRSE}
            RRSE = \sqrt{ \frac{ \sum_{i=1}^n {(p_i - o_i)}^2  }{ \sum_{i=1}^n {(\bar{o} - o_i)}^2 }  }
        \end{equation}
\end{itemize}
where $o_i$ is the current value for the instance $i = {1,...,n}$, $\bar{o}$ is the mean of $o$ and $p_i$ is the obtained prediction.

@@

kNN is the fastest method used in this study in terms of training time, as it 
is the simplest one. However, the model is slow when classifying large number of 
training examples, and it exhibits a poor generalisation ability since it does not 
learn anything from the training data.

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
\hline 
kNN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & \textbf{170.83 $\pm$46.34} & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
\hline 
LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & \textbf{81.8 $\pm$0.08} & \textbf{94.29 $\pm$25.52} & 180.54 $\pm$62.67 & \textbf{50.79 $\pm$8.48} & \textbf{65.62 $\pm$6.25} & 0.040 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo704 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & \textbf{89.2 $\pm$0.07} & \textbf{71.536 $\pm$18.95} & \textbf{123.06 $\pm$42.13} & \textbf{39.43 $\pm$10.58} & \textbf{47.20 $\pm$15.16} & 0.031 $\pm$0.007\tabularnewline
\hline 
kNN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
\hline 
LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLU11 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
\hline 
kNN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & \textbf{1008.39 $\pm$305.87} & 71.41 $\pm$13.95 & \textbf{78.47 $\pm$22.70} & \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF & 65.3 $\pm$0.19 & \textbf{685.56 $\pm$195.28} & 1021.37 $\pm$352.88 & \textbf{69.74 $\pm$16.96} & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
\hline 
LR & \textbf{67.0 $\pm$0.23}\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
\hline 
SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLU11 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
\hline 
kNN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & \textbf{0 $\pm$0.0002}\tabularnewline
\hline 
RF & \textbf{85.6 $\pm$0.08} & \textbf{446.25 $\pm$119.79} & \textbf{673.46 $\pm$189.06} & \textbf{45.38 $\pm$9.78} & \textbf{52.24 $\pm$13.09} & 0.0594 $\pm$0.0049\tabularnewline
\hline 
LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & \textbf{88.0 $\pm$0.13} & \textbf{738.28 $\pm$188.53} & \textbf{1141.79 $\pm$472.025} & \textbf{45.45 $\pm$13.62} & \textbf{47.58 $\pm$24.84} & 0.017 $\pm$0.002\tabularnewline
\hline 
kNN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & \textbf{0.0001 $\pm$0.0002}\tabularnewline
\hline 
RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
\hline 
LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDL929 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & \textbf{89.7 $\pm$0.10} & \textbf{685.67 $\pm$185.99} & \textbf{1116.42 $\pm$478.06} & \textbf{42.09 $\pm$12.8} & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
\hline 
kNN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & \textbf{46.25 $\pm$14.41} & \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
\hline 
LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (CfsSubsetEval-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 81.6 $\pm$0.22 & 15.67 $\pm$6.58 & 25.63 $\pm$11.84 & 47.93 $\pm$18.81 & 60.72 $\pm$31.75 & 0.006 $\pm$0.002\tabularnewline
\hline 
kNN & 75.2 $\pm$0.27 & 15.73 $\pm$7.73 & 26.68 $\pm$14.82 & 48.58 $\pm$24.77 & 66.23 $\pm$48.59 & \textbf{0.0001 $\pm$0.0003}\tabularnewline
\hline 
RF & 75.1 $\pm$0.26 & \textbf{15.61 $\pm$7.19} & 26.83 $\pm$13.36 & \textbf{47.38 $\pm$20.10} & 64.65 $\pm$38.66 & 0.0224 $\pm$0.0027\tabularnewline
\hline 
LR & 81.6 $\pm$0.22 & 15.67 $\pm$6.55 & \textbf{25.49 $\pm$11.63} & 47.97 $\pm$18.85 & \textbf{60.28 $\pm$30.62} & 0.0002 $\pm$0.0004\tabularnewline
\hline 
SVM & \textbf{81.8 $\pm$0.21} & 17.71 $\pm$9.70 & 31.95 $\pm$19.26 & 50.07 $\pm$14.93 & 65.12 $\pm$16.36 & 0.013 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}

\begin{table}[!ht]
\caption{Predicting Total sales for PublishingCo-UDLW12 (SOM-FS). Best values in bold.}
\centering{}%
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & \textbf{86.0 $\pm$0.19} & 13.84 $\pm$6.75 & 23.94 $\pm$11.64 & 41.65 $\pm$17.56 & 55.44 $\pm$27.13 & 0.006 $\pm$0.001\tabularnewline
\hline 
kNN & 74.0 $\pm$0.29 & 15.93 $\pm$8.52 & 28.28 $\pm$16.28 & 48.83 $\pm$25.89 & 68.75 $\pm$48.85 & \textbf{0 $\pm$0.0002}\tabularnewline
\hline 
RF & 85.5 $\pm$0.19 & \textbf{13.66 $\pm$6.47} & \textbf{22.51 $\pm$11.03} & \textbf{41.38 $\pm$17.87} & \textbf{52.20 $\pm$27.09} & 0.026 $\pm$0.0019\tabularnewline
\hline 
LR & 85.4 $\pm$0.21 & 14.59 $\pm$7.13 & 24.40 $\pm$12.87 & 44.81 $\pm$23.65 & 57.73 $\pm$38.63 & 0.0003 $\pm$0.0005\tabularnewline
\hline 
SVM & 84.4 $\pm$0.18 & 14.18 $\pm$7.96 & 26.49 $\pm$16.54 & 40.93 $\pm$16.65 & 54.37 $\pm$20.00 & 0.01 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
}
\end{table}
